%%
%% Copyright (c) 2019-2020 Qian Sun <sqandzxy@gmail.com>
%%
%%

% English version
\documentclass{resume}
\pagestyle{fancy}

\newcommand{\Matlab}{\textsc{Matlab}\textsuperscript{\textregistered} }
\newcommand{\Ansys}{\textsc{Ansys}\textsuperscript{\textregistered} }
\newcommand{\Mathematica}{\textsc{Mathematica}\textsuperscript{\textregistered} }
\newcommand{\Microsoft}{\textsc{Microsoft}\textsuperscript{\textregistered} }
\newcommand{\Solidworks}{\textsc{Solidworks}\textregistered }

% File information shown at the footer of the last page

\name{Qian}{Sun}

\keywords{Matlab, Mathematica, Programming, Construction, Material, Modalanalyse}

% \tagline{\icon{\faBinoculars}} <position-to-look-for>}
% \tagline{<current-position>}

% \photo{<height>}{<filename>}

\profile{
  \mobile{+49 0152-5754-1682}
  \email{sqandzxy@gmail.com}
  \github{sq43793911} \\
  \university{Techinische Universität Bergakademie Freiberg}
  \degree{Master of Science}\\
  \birthday{1991 September}
  \home{Deutschland \textbullet Freiberg}
  % Custom information:
  % \icontext{<icon>}{<text>}
  % \iconlink{<icon>}{<link>}{<text>}
}

\begin{document}
\makeheader

\bigskip

%======================================================================
% Summary & Objectives
%======================================================================
%Vehicle Engineering (Material and Structure Direction) graduate student with good foundations in physics, mathematics, and materials science. Proficient in structural modeling, analysis and Modal-analysis, enthusiastic about computer and network technologies, proficient in using Linux, SSH, Git and other common platforms and tools.
%Proficient in scientific computing software, Matlab and Mathematica programming, skilled in finite element analysis software such as Ansys.

\bigskip

%======================================================================
\sectionTitle{Competences \& Languages}{\faWrench}
%======================================================================
\begin{spacing}{1.4}
\begin{competences}[10em]
  \comptence{Area of expertise}{
   {\large  \textbf{New-energy vehicles}, \quad \textbf{FEM}, \quad \textbf{Modalanalysis}, \quad  \textbf{Light-weight manufacture}, \quad MCU-System}
  }
  \comptence{ Programming}{%
    {\large \textbf{\Matlab}, \quad \Mathematica, \quad R, \quad Python\textregistered, \quad C}
  }
\medskip
  \comptence{ Tools}{%
       {\large \textbf{\Ansys} Products, \quad \textbf{\Solidworks}, \quad Git, \quad \textbf{\LaTeX}, \quad \Microsoft \textbf{Office}, \quad Freescale\textregistered \textbf{CodeWarrior}, \quad IAR\textregistered Embedded Workbench}
  }

  \comptence{\icon{\faLanguage}  Languages}{
  	{\large \textbf{Germany} --- C1;  \quad   \textbf{English} --- B1}
  }
\end{competences}
\end{spacing}

%======================================================================
\sectionTitle{Education}{\faGraduationCap}
%======================================================================
\begin{spacing}{1.3}
	\begin{educations}
		\education%
		{{\large 07.2014}}%
		[{\large 09.2010}]%
		{{\large Liaocheng University}}%
		{{\large School of Mechanical and Automotive Engineering}}%
		{\textbf{{\large Automotive Engineering}}}%
		{{\large Bachelor}}
		
		\separator{1ex}
		
		\education%
		{{\large 07.2020}}%
		[{\large 10.2016}]%
		{{\large Technische Universität Bergakademie Freiberg}}%
		{{\large Faculty 5 - Materials Science and Technology}}%
		{\textbf{{\large Automotive Construction: Materials and Components}}}%
		{{\large Master}}
	\end{educations}
\end{spacing}

\bigskip

%======================================================================
\sectionTitle{Skills}{\faCogs}
%======================================================================
\begin{itemize}
	\setlength{\itemsep}{4pt}

	\item {\large \textit{\underline{Vehicle technology}}\hspace{1mm}:}\\[1.5mm]
	{\large \textbf{Light-weight manufacture}, \hspace{1mm} \textbf{New energy vehicle technology}, \hspace{1mm} Automotive
		Lightweight Technology}
	
	\item {\large \textit{\underline{Materials engineering}}\hspace{1mm}:}\\[1.5mm]
	{\large \textbf{High temperature materials technology}, \hspace{1mm} Material processing and foundry, \hspace{1mm} Bionics}
	
	\item {\large \textit{\underline{Mechanics and Dynamics}}\hspace{1mm}:} \\[1.5mm]
	{\large \textbf{Modalanalysis},\hspace{1mm} Structural analysis and simulation,\hspace{1mm} Dynamics analysis and vibration simulation}
	
	\item {\large \textit{\underline{Computer science}}\hspace{1mm}:} \\[1.5mm]
	{\large \textbf{Design and debugging of MCU-system}, Design and debugging of control system.}
	
	\item {\large \textit{\underline{Others}}\hspace{1mm}:} \\[1.5mm]
	{\large \textbf{Optimization design},\hspace{1mm} Neural-network and deep learning, \hspace{1mm} Big-data-analysis.}
	
\end{itemize}

%======================================================================
\sectionTitle{Personal Projects}{\faCode}
%======================================================================
\begin{itemize}
	\begin{spacing}{1.4}
	\setlength{\itemsep}{12pt}
	\item 
	\link{https://github.com/sq43793911/Masterarbeit_public}{\texttt{\textbf{\underline{{\large Master thesis:}}}}} (\textit{Matlab\textregistered}, \textit{Mathematica\textregistered}, \textit{Ansys\textregistered}, \textit{Solidworks\textregistered}, \textit{\LaTeX}, \textit{FEM}, \textit{PULSE LabShop}, \textit{ME'scopeVES})\\[1mm]
	\link{https://github.com/sq43793911/Masterarbeit_public}{\githubSymbol $ \Rightarrow $ https://github.com/sq43793911/Masterarbeit\_public }\\
	\link{https://github.com/sq43793911/Masterarbeit_public}{\color{black} {\large \textbf{Experimental and simulative modal analysis of a tool shank during HSC milling and the influence of an eccentricity error.} In the context of the advertised work, the dynamic behaviour of a tool shaft in HSC milling must be investigated. The influence of an unbalance (eccentricity) should be in the foreground. In addition to the simulation, an experimental study will also be carried out. For this purpose, an experimental device must be designed, manufactured and put into operation. The FE simulation is performed with Matlab. In addition, the CAD program Solidworks is used to design the components. PULSE LabShop and ME'scopeVES are used for the measurement.}}
	
	\item \link{https://github.com/sq43793911/Projektarbeit_public}{\texttt{\textbf{\underline{{\large Project work:}}}}} (\textit{Matlab\textregistered, Mathematica\textregistered, Ansys\textregistered, \LaTeX, FEM})\\[1mm]
	\link{https://github.com/sq43793911/Projektarbeit_public}{\githubSymbol $ \Rightarrow $ https://github.com/sq43793911/Projektarbeit\_public }\\
	\link{https://github.com/sq43793911/Projektarbeit_public}{\color{black} {\large \textbf{Modalanalysis with the Finite-Element-Method.} As part of the advertised work, a program for numerical modal analysis using the finite element method is to be developed. The FE simulation is performed with Matlab. In addition, the FE-software Ansys is used to compare the results.}}
	
	\item \link{https://github.com/sq43793911/Intelligent-Algorithms}{\texttt{\textbf{\underline{{\large Research project for intelligent algorithms:}}}}}(\textit{Matlab\textregistered})\\[1mm]
	\link{https://github.com/sq43793911/Intelligent-Algorithms}{\githubSymbol $ \Rightarrow $ https://github.com/sq43793911/Intelligent-Algorithms }\\
	\link{https://github.com/sq43793911/Intelligent-Algorithms}{\color{black} {\large $ \mathbf{a)}  $ Four popular intelligent optimization algorithms (genetic, ant colonial, immune, tabular table algorithm) are used to analyze the TSP and the advantages and disadvantages of different algorithms and their application value are compared. \\[1mm]
			$ \mathbf{b)}  $ The genetic algorithm is used to optimize the analysis of cost management for warehouse storage and ordering. \\[1mm]
			$ \mathbf{c)}  $ Based on Matlab's Classifacation Learner Toolbox, kNN(k Nearest Neighbour Classification Algorithm) and cluster analysis algorithms are studied and practiced, which are commonly used in data mining.}}
	
	\item \link{https://github.com/sq43793911/Balance_Car}{\texttt{\textbf{\underline{{\large Balance Car:}}}}}(\textit{Freescale\textregistered CodeWarrior, Freescale\textregistered S12X, C, CCD}) \\[1mm]
	\link{https://github.com/sq43793911/Balance_Car}{\githubSymbol $ \Rightarrow $ https://github.com/sq43793911/Balance\_Car }\\
	\link{https://github.com/sq43793911/Balance_Car}{\color{black} {\large A two-wheeled self-balance vehicle designed and manufactured on the requirements of the Freescale Smart Car Cup and with automatic lane detection and control functions. The control system is based on the Freescale S12X microcontroller and uses a CCD camera for track detection. }}
	
	\item \link{https://github.com/sq43793911/Construction_Analysis}{\texttt{\textbf{\underline{{\large Analyzing of vibration systems:}}}}}(\textit{Matlab\textregistered})\\[1mm]
	\link{https://github.com/sq43793911/Construction_Analysis}{\githubSymbol $ \Rightarrow $ https://github.com/sq43793911/Construction\_Analysis }\\
	\link{https://github.com/sq43793911/Construction_Analysis}{\color{black} {\large Undamped vibrations, damped vibrations, the time domain properties of the Maxwell model and the reaction properties after the excitation are analyzed and the corresponding images are generated.}}
	
	\item \link{https://github.com/sq43793911/resume}{\texttt{\textbf{\underline{{\large Resume:}}}}}(\textit{\LaTeX})\\[1mm]
	\link{https://github.com/sq43793911/resume}{\githubSymbol $ \Rightarrow $ https://github.com/sq43793911/resume }\\
	\link{https://github.com/sq43793911/resume}{\color{black} {\large This resume was crafted using \LaTeX  and learned the basic functions and usage of \LaTeX.}}
\end{spacing}

\end{itemize}

\clearpage

\end{document}
